Exploring the structure of the bound proton with Deeply Virtual Compton Scattering

### 2019-03-10 eg6-letters/incoherent/incoherent_prl.tex
fix spelling

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. 
First, events were selected with $Q^2$ grater than $1$ GeV$^2$ and the 
$\gamma^*p$ invariant mass ($W=\sqrt{(q+p)^2}$, assuming that the initial 
nucleon is at rest) greater than $2$ GeV. This is a commonly accepted region of 
kinematics used by the previous DVCS experiments to ensure the applicability of 
the DVCS handbag diagram and avoid the nucleon resonance region. The squared 
transferred momentum to the recoil proton $t$, calculated from the 
four-momentum vectors of the incoming and outgoing photons, was required to be 
greater than a minimum kinematically allowed value ($t_{min}$) at given $Q^2$ 
and $W$ defined as: \begin{equation}
t_{min} 
   =-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}},
\end{equation}
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass. This cut was applied to avoid accepting events that appear in  
unphysical regions of kinematics due to detector resolution and radiative 
effects.  We specifically use the kinematics of the photons to determine $t$ 
because the initial proton kinematics is unknown due to Fermi motion.

>>>>

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. 
First, events were selected with $Q^2$ greater than $1$ GeV$^2$ and the 
$\gamma^*p$ invariant mass ($W=\sqrt{(q+p)^2}$, assuming that the initial 
nucleon is at rest) greater than $2$ GeV. This is a commonly accepted region of 
kinematics used by the previous DVCS experiments to ensure the applicability of 
the DVCS handbag diagram and avoid the nucleon resonance region. The squared 
transferred momentum to the recoil proton $t$, calculated from the 
four-momentum vectors of the incoming and outgoing photons, was required to be 
greater than a minimum kinematically allowed value ($t_{min}$) at given $Q^2$ 
and $W$ defined as: \begin{equation}
t_{min} 
   =-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}},
\end{equation}
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass. This cut was applied to avoid accepting events that appear in  
unphysical regions of kinematics due to detector resolution and radiative 
effects.  We specifically use the kinematics of the photons to determine $t$ 
because the initial proton kinematics is unknown due to Fermi motion.
